### 2022-10-19 draft/draft.Rmd
almost done

In this setting, if we know the labels $z_1, ..., z_n$, then for each $k$^th^ subsample for which $z_i = k$, we can fit the curve $\hat{g}_k$ (up to an indefinite orthogonal transformation). 
On the other hand, if we know the curves $g_1, ..., g_K$, then we can assign each embedding vector $\hat{x}_i$ the predicted label $\hat{z}_i$ based on which curve it is closest to. 
This lends itself to an alternating coordinate descent algorithm in which we alternate between fitting curves and assigning labels at each iteration (algorithm \ref{alg:kcurves}). 
We call this algorithm $K$-curves clustering. 
In this algorithm, the loss function that we wish to minimize is
\begin{equation}
\label{eq:kcurves-loss}
L(z_1, ..., z_n, g_1, ..., g_n; X) = \sum_{k=1}^K \sum_{i: z_i = k} \|x_i - g_k(t_i)\|^2
\end{equation}

@@

\begin{theorem}
\label{thm:kcurves-semisupervised}
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$ and its density function is such that $f(t) > a > 0$ for every $t \in [0, 1]$, and each $g_k$ is is a Bezier curve of order $R$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_n; X) \stackrel{p}{\to} 0,$$
where $L$ is defined as in equation \ref{eq:kcurves-loss}. 
\end{theorem}

@@

In the final example, we examined the *Drosophila* connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}. 
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types, Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons. 
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere. 
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

@@

\begin{proof}[Proof of theorem \ref{thm:kcurves-semisupervised}]
\end{proof}

>>>>

In this setting, if we know the labels $z_1, ..., z_n$, then for each $k$^th^ subsample for which $z_i = k$, we can fit the curve $\hat{g}_k$ (up to an indefinite orthogonal transformation). 
On the other hand, if we know the curves $g_1, ..., g_K$, then we can assign each embedding vector $\hat{x}_i$ the predicted label $\hat{z}_i$ based on which curve it is closest to. 
This lends itself to an alternating coordinate descent algorithm in which we alternate between fitting curves and assigning labels at each iteration (algorithm \ref{alg:kcurves}). 
We call this algorithm $K$-curves clustering. 
In this algorithm, the loss function that we wish to minimize is
\begin{equation}
\label{eq:kcurves-loss}
L(z_1, ..., z_n, g_1, ..., g_n; X) = \frac{1}{n} \sum_{k=1}^K \sum_{i: z_i = k} \|x_i - g_k(t_i)\|^2
\end{equation}

@@

\begin{theorem}
\label{thm:kcurves-semisupervised}
Let $A \sim \MBM(\{\alpha_1, ..., \alpha_K\}, \{F, ..., F\}, \{g_1, ..., g_K\}; \rho_n)$ such that $F$ has support $[0, 1]$, and each $g_k(t) = g(t; p_k)$ is is a Bezier curve of order $R$. 
Suppose that for each community $k$, we have labels for at least $R + 1$ vertices. 
Then if $n \rho_n = \omega(\log^{4c} n)$, as $n \to \infty$, the estimates outputted by $K$-curves clustering are such that 
$$L(\hat{z}_1, ..., \hat{z}_n, \hat{g}_1, ..., \hat{g}_n; X) \stackrel{p}{\to} 0,$$
where $L$ is the loss function defined in equation (\ref{eq:kcurves-loss}). 
\end{theorem}

@@

In the final example, we examined the *Drosophila* connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}. 
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere. 
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

@@

\begin{proof}[Proof of theorem \ref{thm:kcurves-semisupervised}]
Let $\hat{X}$ with rows $\hat{x}_i^\top$ be the ASE of $A$ drawn from an MBM in which each $g_k(t) = g(t; p_k)$ is a Bezier curve of order $R$. 
Define the ASE error as $\epsilon_i = \|Q \hat{x}_i - x_i\|$ and $\epsilon = \max_i \epsilon_i$ where $Q$ is the appropriate indefinite orthogonal transformation for the ASE. 
By \citet{rubindelanchy2017statistical}, $\epsilon = O_P \bigg(\frac{\log^c n}{\sqrt{n}} \bigg)$.

Since $x_i = g(t_i; p_{z_i})$, $\|Q \hat{x}_i - g(t_i; p_{z_i})\| < \epsilon$.

The statement of the theorem assumes that for each community $k$, there at least $R + 1$ points with known label $k$. 
For simplicity, suppose we have exactly $R + 1$ (if there are more, then discard the rest). 
Then for each community $k$, it is possible to fit a polynomial of order $R$ that goes through each of the $R + 1$ known points exactly (see appendix B), yielding $g(t; \hat{p}_k)$, where $\hat{p}_k$ are the fitted coefficients of the Bezier polynomial. 
Use the fitted Bezier curves to define $\delta_k(t) = \|Q g(t; \hat{p}_k) - g(t; p_k)\|$, $\delta_k = \max_t \delta_k(t)$, and $\delta = \max_k \delta_k$. 
Since $P(\epsilon < M n^{-1/2} \log^c n) \to 1$ for constants $M, c > 0$, 
$P(\delta_k < M n^{-1/2} \log^c n) \to 1$ for each $k$. 
Since $\epsilon_i$ describes the error between each embedding point and its corresponding latent vertex, and $\delta_k(t_i)$ describes the error between the fitted curve and its corresponding true curve in the latent space, 
$L < \frac{1}{n} \sum_i \epsilon_i + \delta_{z_i}(t_i) < \frac{1}{n} n (\epsilon + \delta) = \epsilon + \delta$. 
Then $P(L < 2 M n^{-1/2} \log^c n) > P(\epsilon + \delta < 2 M n^{-1/2} \log^c n) \to 1$ as $n \to \infty$.

\end{proof}

### 2022-10-19 draft/draft.tex
almost done

In this setting, if we know the labels \(z_1, ..., z_n\), then for each \(k\)\textsuperscript{th} subsample for which \(z_i = k\), we can fit the curve \(\hat{g}_k\) (up to an indefinite orthogonal transformation).
On the other hand, if we know the curves \(g_1, ..., g_K\), then we can assign each embedding vector \(\hat{x}_i\) the predicted label \(\hat{z}_i\) based on which curve it is closest to.
This lends itself to an alternating coordinate descent algorithm in which we alternate between fitting curves and assigning labels at each iteration (algorithm \ref{alg:kcurves}).
We call this algorithm \(K\)-curves clustering.
In this algorithm, the loss function that we wish to minimize is
\begin{equation}
\label{eq:kcurves-loss}
L(z_1, ..., z_n, g_1, ..., g_n; X) = \sum_{k=1}^K \sum_{i: z_i = k} \|x_i - g_k(t_i)\|^2
\end{equation}

@@

In the final example, we examined the \emph{Drosophila} connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}.
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types, Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons.
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere.
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

@@

>>>>

In this setting, if we know the labels \(z_1, ..., z_n\), then for each \(k\)\textsuperscript{th} subsample for which \(z_i = k\), we can fit the curve \(\hat{g}_k\) (up to an indefinite orthogonal transformation).
On the other hand, if we know the curves \(g_1, ..., g_K\), then we can assign each embedding vector \(\hat{x}_i\) the predicted label \(\hat{z}_i\) based on which curve it is closest to.
This lends itself to an alternating coordinate descent algorithm in which we alternate between fitting curves and assigning labels at each iteration (algorithm \ref{alg:kcurves}).
We call this algorithm \(K\)-curves clustering.
In this algorithm, the loss function that we wish to minimize is
\begin{equation}
\label{eq:kcurves-loss}
L(z_1, ..., z_n, g_1, ..., g_n; X) = \frac{1}{n} \sum_{k=1}^K \sum_{i: z_i = k} \|x_i - g_k(t_i)\|^2
\end{equation}

@@

In the final example, we examined the \emph{Drosophila} connectome graph \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2017statistical}, \citet{https://doi.org/10.48550/arxiv.1705.03297}, and \citet{SannaPassino2022}.
In this graph, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons).
In our analysis, we only considered neurons labeled as Kenyon Cells and Projection Neurons in the right hemisphere.
The resulting graph is illustrated in figure \ref{fig:mbconnectome-graph}.

@@

\begin{proof}[Proof of theorem \ref{thm:kcurves-semisupervised}]
Let $\hat{X}$ with rows $\hat{x}_i^\top$ be the ASE of $A$ drawn from an MBM in which each $g_k(t) = g(t; p_k)$ is a Bezier curve of order $R$. 
Define the ASE error as $\epsilon_i = \|Q \hat{x}_i - x_i\|$ and $\epsilon = \max_i \epsilon_i$ where $Q$ is the appropriate indefinite orthogonal transformation for the ASE. 
By \citet{rubindelanchy2017statistical}, $\epsilon = O_P \bigg(\frac{\log^c n}{\sqrt{n}} \bigg)$.

Since $x_i = g(t_i; p_{z_i})$, $\|Q \hat{x}_i - g(t_i; p_{z_i})\| < \epsilon$.

The statement of the theorem assumes that for each community $k$, there at least $R + 1$ points with known label $k$. 
For simplicity, suppose we have exactly $R + 1$ (if there are more, then discard the rest). 
Then for each community $k$, it is possible to fit a polynomial of order $R$ that goes through each of the $R + 1$ known points exactly (see appendix B), yielding $g(t; \hat{p}_k)$, where $\hat{p}_k$ are the fitted coefficients of the Bezier polynomial. 
Use the fitted Bezier curves to define $\delta_k(t) = \|Q g(t; \hat{p}_k) - g(t; p_k)\|$, $\delta_k = \max_t \delta_k(t)$, and $\delta = \max_k \delta_k$. 
Since $P(\epsilon < M n^{-1/2} \log^c n) \to 1$ for constants $M, c > 0$, 
$P(\delta_k < M n^{-1/2} \log^c n) \to 1$ for each $k$. 
Since $\epsilon_i$ describes the error between each embedding point and its corresponding latent vertex, and $\delta_k(t_i)$ describes the error between the fitted curve and its corresponding true curve in the latent space, 
$L < \frac{1}{n} \sum_i \epsilon_i + \delta_{z_i}(t_i) < \frac{1}{n} n (\epsilon + \delta) = \epsilon + \delta$. 
Then $P(L < 2 M n^{-1/2} \log^c n) > P(\epsilon + \delta < 2 M n^{-1/2} \log^c n) \to 1$ as $n \to \infty$.

\end{proof}
